Improving Usability of Remote Access to Sensitive Data

### 2014-07-29 ccsw14/paper.tex
added figures and more small fixes

\usepackage{epstopdf}
\usepackage{datetime}

@@

Data Capsules makes heavy use of virtualization.  For each system user, there
are one or more corresponding VMs.  Multiple VMs per user may be useful in
situations where there is a large repository of data that is separated into
multiple corpora each with their own access permissions.  In this case, a user
could potentially have multiple VMs, each with access to a different corpus.
However, the handling of such an access permissions system is outside the scope
of this paper.

@@

Beyond securing the connection, we are currently investigating methods for
securing the end client device using the Trusted Platform Module (TPM) on an end
user's device to remotely attest that the end client is secure.  We envision the
final implementation will consist of a USB thumb drive containing a barebones
Linux operating system with an installed VNC client, and will use the TPM's
features to perform a measured boot of Linux and the VNC client.  Users will
plug in the USB drive to their device and boot into the secure environment in
order to access their Data Capsules VMs.  In this way, we hope to greatly raise
the bar for a malicious attacker who wishes to gain access to sensitive data,
while preserving a reasonably uncumbersome method for access to the end user.

>>>>

\usepackage{url}
\usepackage{epstopdf}
\usepackage{datetime}

@@

\begin{figure}[ht!]
\center
\includegraphics[width=3.0in]{figures/architecture}

\caption{A Data Capsules virtual machine runs in one of two modes.  In
maintenance mode, VM state such as memory, CPU and disk state persists across
shutdowns and mode transitions.  In secure mode, this virtual state is lost
once a user returns to maintenance mode. The only exception is any data stored
in the user's secure storage volume, which is attached to the VM only when the
user enters secure mode.}

\label{fig:architecture}
\end{figure}

Data Capsules features an architecture, illustrated in Figure
\ref{fig:architecture}, that makes heavy use of virtualization.  For each
system user, there are one or more corresponding VMs.  Multiple VMs per user
may be useful in situations where there is a large repository of data that is
separated into multiple corpora each with their own access permissions.  In
this case, a user could potentially have multiple VMs, each with access to a
different corpus.  However, the handling of such an access permissions system
is outside the scope of this paper.

@@

Beyond securing the connection, we are currently investigating methods for
securing the end client device using the Trusted Platform Module (TPM)
\cite{tpm} on an end user's device to remotely attest that the end client is
secure.  We envision the final implementation will consist of a USB thumb drive
containing a barebones Linux operating system with an installed VNC client, and
will use the TPM's features to perform a measured boot of Linux and the VNC
client.  Users will plug in the USB drive to their device and boot into the
secure environment in order to access their Data Capsules VMs.  In this way, we
hope to greatly raise the bar for a malicious attacker who wishes to gain
access to sensitive data, while preserving a reasonably uncumbersome method for
access to the end user.
